Thesis Title

### 2022-05-23 chapters/chapter_4.tex
mv chap 4 and 7 tables to tables folder

\begin{table}[h!]
\caption{DEN-IM’s workflow comparison with different tools for the identification and genotyping of DENV from sequencing data.}
\label{tab:ch4_table1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lcccccc@{}}
\toprule
\textbf{Tool} &
  \textbf{Quality Control} &
  \textbf{DENV Sequence Retrieval} &
  \textbf{Assembly} &
  \textbf{Typing} &
  \textbf{Phylogeny} &
  \textbf{Report} \\ \midrule
DEN-IM &
  \checkmark &
  \checkmark &
  \checkmark &
  \checkmark &
  \checkmark &
  \begin{tabular}[c]{@{}c@{}}\checkmark (one report \\ with all samples \\ analysed)\end{tabular} \\
VIP &
  \checkmark &
  \checkmark$^1$ &
  \checkmark &
  X &
  \checkmark &
  \checkmark \\
VirusTAP &
  \checkmark &
  \checkmark$^1$ &
  \checkmark &
  X &
  X &
  \begin{tabular}[c]{@{}c@{}}\checkmark (web-based, \\ one per sample, \\ downloadable)\end{tabular} \\
drVM &
  \checkmark &
  \checkmark$^1$ &
  \checkmark &
  X &
  X &
  X \\
\begin{tabular}[c]{@{}l@{}}GenomeDetective \\ Virus Tool\end{tabular} &
  \checkmark &
  X &
  \checkmark &
  X &
  X &
  \begin{tabular}[c]{@{}c@{}}\checkmark (web-based, \\ one per sample)\end{tabular} \\
\begin{tabular}[c]{@{}l@{}}GenomeDetective \\ Dengue Typing Tool\end{tabular} &
  X &
  X &
  X &
  \checkmark$^2$ &
  X &
  \begin{tabular}[c]{@{}c@{}}\checkmark (web-based, \\ one per sample)\end{tabular} \\ \bottomrule
\end{tabular}%
}
\item $^1$ Targeted for viral sequences, but not specific for DENV
\item $^2$ Sequence file can be received from GenomeDetective Virus Tool, as well as independently uploaded
\end{table}

@@

The accession numbers for the 132 samples, belonging to zika virus (ZKV), chikungunya virus (CHIKV) and yellow fever virus (YFV) amplicon and metagenomic datasets are available as supplemental material (Table S4). As with the amplicon sequencing dataset, the list of Run Accession IDs was obtained with NCBI’s RunSelector and the raw data was downloaded with the GetSeqENA tool (https://github.com/B-UMMI/getSeqENA).

@@

\begin{table}[h!]
\caption{Collection date, serotype confirmation and run accession identifier for the metagenomic sequencing dataset.}
\label{tab:chap4_s1}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
\toprule
\textbf{Sample} & \textbf{Collection   Date} & \textbf{Source} & \textbf{Serotype   (qPCR)} & \textbf{Serotype} & \textbf{Genotype}            & \textbf{Run Accession} \\ \midrule
91-0104          & 21/9/2015  & plasma & 2 & 2 & III(AsianAmerican) & SRR8842525 \\
91-0105          & 22/9/2015  & plasma & 2 & 2 & III(AsianAmerican) & SRR7252349 \\
91-0115          & 30/9/2015  & plasma & 3 & - & -                  & SRR7252368 \\
91-0118          & 5/10/2015  & plasma & 3 & 3 & III                & SRR7252362 \\
91-0132          & 19/10/2015 & plasma & 1 & 1 & V                  & SRR8883926 \\
91-0135          & 27/10/2015 & plasma & 2 & 2 & III(AsianAmerican) & SRR9004764 \\
92-1001          & 2/10/2015  & plasma & 1 & - & -                  & SRR7252337 \\
92-1094          & 16/10/2015 & plasma & 2 & 2 & III(AsianAmerican) & SRR8842524 \\
CC0007           & 31/8/2010  & serum  & 2 & 2 & III(AsianAmerican) & SRR7252354 \\
CC0009           & 31/8/2010  & serum  & 3 & 3 & III                & SRR8842527 \\
CC0010           & 27/8/2010  & serum  & 3 & 3 & III                & SRR7252358 \\
CC0011           & 27/8/2010  & serum  & 3 & 3 & III                & SRR8842526 \\
CC0030a          & 1/9/2010   & serum  & 4 & 4 & II                 & SRR7252356 \\
CC0030b          & 1/9/2010   & serum  & 4 & 4 & II                 & SRR7252355 \\
CC0031           & 2/9/2010   & serum  & 2 & 2 & III(AsianAmerican) & SRR8842521 \\
CC0061           & 20/1/2011  & serum  & 4 & 4 & II                 & SRR8842520 \\
CC0066           & 11/10/2011 & serum  & 4 & 4 & II                 & SRR8842523 \\
CC0067           & 18/10/2011 & serum  & 4 & 4 & II                 & SRR8842522 \\
CC0116           & 29/3/2012  & serum  & 4 & 4 & II                 & SRR8842519 \\
CC0150           & 9/5/2012   & serum  & 2 & 2 & III(AsianAmerican) & SRR8842518 \\
CC0186           & 17/7/2012  & serum  & 4 & 4 & II                 & SRR9004763 \\
UCUG0186         & 30/8/2010  & serum  & 4 & 4 & II                 & SRR8842528 \\
Negative Control & -          & -      & - & - & -                  & SRR8842530 \\
Positive Control & -          & -      & 2 & 2 & V(AsianI)          & SRR8886136 \\
Spiked   sample & -                          & -               & 1,2,3,4                    & 1,2,3,4           & V,III(Asian American),III,II & SRR8842529             \\ \bottomrule
\end{tabular}%
}
\end{table}

@@

\begin{longtable}{@{}lllll@{}}
\caption{Run accession ID, BioProject SRA Study ID, source and organism present for each sample of the negative control dataset (ZKV – zika virus, CHIKV – chikungunya virus, YFV – yellow fever virus).}
\label{tab:chap4_s2}\\
\toprule
Run ID     & Bioproject  & SRA Study & Source                & Organism \\ \midrule
SRR8031152 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8062732 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8031153 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8063606 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8063603 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8063605 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8031155 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8031154 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8063604 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR8062733 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR7985391 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR7985394 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR7985620 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & CHIKV    \\
SRR7985390 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR7985392 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR7985621 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & CHIKV    \\
SRR5179639 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179637 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179646 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR7985389 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR7985622 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & CHIKV    \\
SRR7985619 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & CHIKV    \\
SRR5179667 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179653 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR7985393 & PRJNA494391 & SRP163225 & Shotgun Metagenomic   & ZKV      \\
SRR5179638 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179636 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179666 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179650 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179649 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179643 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179635 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179645 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179642 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179644 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179647 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179641 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179640 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179652 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179648 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR5179651 & PRJNA361543 & SRP096859 & Amplicon Metagenomics & YFV      \\
SRR9020503 & PRJNA541092 & SRP195668 & Amplicon Metagenomics & CHIKV    \\
SRR9020505 & PRJNA541093 & SRP195669 & Amplicon Metagenomics & CHIKV    \\
SRR9020506 & PRJNA541094 & SRP195670 & Amplicon Metagenomics & CHIKV    \\
SRR9020509 & PRJNA541095 & SRP195671 & Amplicon Metagenomics & CHIKV    \\
SRR9020511 & PRJNA541096 & SRP195672 & Amplicon Metagenomics & CHIKV    \\
SRR9020513 & PRJNA541097 & SRP195673 & Amplicon Metagenomics & CHIKV    \\
SRR9020514 & PRJNA541098 & SRP195674 & Amplicon Metagenomics & CHIKV    \\
SRR9020516 & PRJNA541099 & SRP195675 & Amplicon Metagenomics & CHIKV    \\
SRR9020518 & PRJNA541100 & SRP195676 & Amplicon Metagenomics & CHIKV    \\
SRR9020520 & PRJNA541101 & SRP195677 & Amplicon Metagenomics & CHIKV    \\
SRR9020521 & PRJNA541102 & SRP195678 & Amplicon Metagenomics & CHIKV    \\
SRR9020523 & PRJNA541103 & SRP195679 & Amplicon Metagenomics & CHIKV    \\
SRR9020525 & PRJNA541104 & SRP195680 & Amplicon Metagenomics & CHIKV    \\
SRR9020527 & PRJNA541105 & SRP195681 & Amplicon Metagenomics & CHIKV    \\
SRR9020529 & PRJNA541106 & SRP195682 & Amplicon Metagenomics & CHIKV    \\
SRR9020530 & PRJNA541107 & SRP195683 & Amplicon Metagenomics & CHIKV    \\
SRR9020532 & PRJNA541108 & SRP195684 & Amplicon Metagenomics & CHIKV    \\
SRR9020534 & PRJNA541109 & SRP195685 & Amplicon Metagenomics & CHIKV    \\
SRR9020537 & PRJNA541110 & SRP195686 & Amplicon Metagenomics & CHIKV    \\
SRR9020539 & PRJNA541111 & SRP195687 & Amplicon Metagenomics & CHIKV    \\
SRR9020541 & PRJNA541112 & SRP195688 & Amplicon Metagenomics & CHIKV    \\
SRR9020542 & PRJNA541113 & SRP195689 & Amplicon Metagenomics & CHIKV    \\
SRR9020504 & PRJNA541114 & SRP195690 & Amplicon Metagenomics & CHIKV    \\
SRR9020507 & PRJNA541115 & SRP195691 & Amplicon Metagenomics & CHIKV    \\
SRR9020508 & PRJNA541116 & SRP195692 & Amplicon Metagenomics & CHIKV    \\
SRR9020510 & PRJNA541117 & SRP195693 & Amplicon Metagenomics & CHIKV    \\
SRR9020512 & PRJNA541118 & SRP195694 & Amplicon Metagenomics & CHIKV    \\
SRR9020515 & PRJNA541119 & SRP195695 & Amplicon Metagenomics & CHIKV    \\
SRR9020517 & PRJNA541120 & SRP195696 & Amplicon Metagenomics & CHIKV    \\
SRR9020519 & PRJNA541121 & SRP195697 & Amplicon Metagenomics & CHIKV    \\
SRR9020522 & PRJNA541122 & SRP195698 & Amplicon Metagenomics & CHIKV    \\
SRR9020524 & PRJNA541123 & SRP195699 & Amplicon Metagenomics & CHIKV    \\
SRR9020526 & PRJNA541124 & SRP195700 & Amplicon Metagenomics & CHIKV    \\
SRR9020528 & PRJNA541125 & SRP195701 & Amplicon Metagenomics & CHIKV    \\
SRR9020531 & PRJNA541126 & SRP195702 & Amplicon Metagenomics & CHIKV    \\
SRR9020533 & PRJNA541127 & SRP195703 & Amplicon Metagenomics & CHIKV    \\
SRR9020535 & PRJNA541128 & SRP195704 & Amplicon Metagenomics & CHIKV    \\
SRR9020536 & PRJNA541129 & SRP195705 & Amplicon Metagenomics & CHIKV    \\
SRR9020538 & PRJNA541130 & SRP195706 & Amplicon Metagenomics & CHIKV    \\
SRR9020540 & PRJNA541131 & SRP195707 & Amplicon Metagenomics & CHIKV    \\
SRR7369225 & PRJNA47661  & SRP150883 & Shotgun Metagenomic   & ZKV      \\
SRR7369226 & PRJNA47661  & SRP150883 & Shotgun Metagenomic   & ZKV      \\
SRR6505781 & PRJNA431343 & SRP131290 & Shotgun Metagenomic   & ZKV      \\
SRR8260975 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8260976 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8260977 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8260978 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8260979 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8260980 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261322 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261325 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261326 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261329 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261330 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261331 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261332 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261333 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261335 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261336 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261338 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261341 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261342 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261343 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261345 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261346 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261347 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261348 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261352 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261353 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261354 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261355 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261356 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261359 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261360 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261361 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261362 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261364 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261365 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261366 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261367 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261369 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261402 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261404 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261407 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261411 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261412 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261413 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261415 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261416 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV      \\
SRR8261417 & PRJNA314889 & SRP162155 & Shotgun Metagenomic   & ZKV  \bottomrule   
\end{longtable}

\begin{table}[h!]
\caption{Number of raw base pairs, overall alignment rate against the DENV mapping database, estimated coverage depths and serotype and genotype for 25 shotgun metagenomics sequencing samples.}
\label{tab:chap4_s3}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}llllll@{}}
\toprule
Sample                 & Raw Megabases            & \% DENV Reads          & Estimated   coverage depth (times) & Serotype & Genotype    \\ \midrule
91-0104               & 2193.71 & 12.46 & 5944.67  & 2 & III (AsianAmerican) \\
91-0105               & 191.37  & 4.01  & 495.97   & 2 & III (AsianAmerican) \\
91-0115               & 179.24  & 0.05  & 3.74     & - & -                   \\
91-0118               & 195.27  & 1.69  & 86.53    & 3 & III                 \\
91-0132               & 378.21  & 20.02 & 4698.12  & 1 & V                   \\
91-0135               & 91.71   & 21.45 & 1287.52  & 2 & III (AsianAmerican) \\
92-1001   a)          & 163.44  & -     & -        & - & -                   \\
92-1094               & 1197.92 & 8.48  & 4032.21  & 2 & III (AsianAmerican) \\
CC0007                & 252.97  & 3.79  & 383.77   & 2 & III (AsianAmerican) \\
CC0009                & 2055.13 & 9.48  & 8226.27  & 3 & III                 \\
CC0010                & 368.64  & 5.68  & 1197.58  & 3 & III                 \\
CC0011                & 924.69  & 8.38  & 3016.17  & 3 & III                 \\
CC0030a               & 261.12  & 52.52 & 2914.87  & 4 & II                  \\
CC0030b               & 399.04  & 10.51 & 677.96   & 4 & II                  \\
CC0031                & 1572.1  & 68.91 & 52318.33 & 2 & III (AsianAmerican) \\
CC0061                & 1262.83 & 8.97  & 5120.4   & 4 & II                  \\
CC0066                & 1087.45 & 2.8   & 569.7    & 4 & II                  \\
CC0067                & 1022.06 & 5.55  & 2548.84  & 4 & II                  \\
CC0116                & 773.31  & 6.72  & 2313.99  & 4 & II                  \\
CC0150                & 1403.69 & 17.41 & 12065.81 & 2 & III (AsianAmerican) \\
CC0186                & 671.78  & 0.03  & 14.71    & 4 & II                  \\
UCUG0186   b)         & 1116.67 & 0.01  & 5.65     & - & -                   \\
Negative   Control a) & 163.67  & -     & -        & - & -                   \\
Positive   Control     & 443.93                   & 85.38                 & 19362.07                           & 2        & V (Asian I) \\
\multirow{4}{*}{Spike} & \multirow{4}{*}{1518.93} & \multirow{4}{*}{41.7} & \multirow{4}{*}{22289.98}          & 3        & III         \\
                      &         &       &          & 1 & V                   \\
                      &         &       &          & 2 & III (AsianAmerican) \\
                      &         &       &          & 4 & II                 
\end{tabular}%
}
\item a) Failed quality control - No sequence data after quality trimming.
\item b) Failed quality control - Low sequence depth (<10x).
\end{table}

@@

\begin{longtable}{@{}llllll@{}}
\caption{Number of raw base pairs, overall alignment rate, in percentage, for the mapping against the DENV database, number of ORFs recovered, and respective serotype and genotype for 106 paired-end amplicon sequencing samples.}
\label{tab:chap4_s4}\\
\toprule
Sample     & Raw Megabases & \% DENV DNA & CDS Assembly & Serotype & Genotype \\ \midrule
SRR5821157 & 439.35        & 82.56       & consensus    & 3        & III      \\
SRR5821158 & 77.34         & 85.19       & consensus    & 3        & III      \\
SRR5821159 & 68.00         & 91.11       & consensus    & 3        & III      \\
SRR5821160 & 119.54        & 97.77       & consensus    & 3        & III      \\
SRR5821161 & 53.40         & 92.76       & consensus    & 3        & III      \\
SRR5821162 & 49.59         & 99.39       & consensus    & 3        & III      \\
SRR5821163 & 66.43         & 97.78       & consensus    & 3        & III      \\
SRR5821164 & 69.96         & 99.18       & consensus    & 3        & III      \\
SRR5821165 & 75.48         & 98.38       & consensus    & 3        & III      \\
SRR5821166 & 38.99         & 62.03       & de novo      & 3        & III      \\
SRR5821167 & 73.15         & 49.19       & de novo      & 3        & III      \\
SRR5821168 & 49.59         & 99.63       & consensus    & 3        & III      \\
SRR5821169 & 119.39        & 99.74       & de novo      & 3        & III      \\
SRR5821170 & 61.45         & 99.09       & consensus    & 3        & III      \\
SRR5821171 & 61.63         & 98.92       & consensus    & 3        & III      \\
SRR5821172 & 69.86         & 98.96       & de novo      & 3        & III      \\
SRR5821173 & 80.37         & 97.59       & de novo      & 3        & III      \\
SRR5821174 & 37.58         & 76.69       & de novo      & 3        & III      \\
SRR5821175 & 112.70        & 75.55       & de novo      & 3        & III      \\
SRR5821176 & 139.34        & 99.03       & de novo      & 3        & III      \\
SRR5821177 & 41.19         & 44.56       & de novo      & 3        & III      \\
SRR5821178 & 59.03         & 81.06       & de novo      & 3        & III      \\
SRR5821179 & 95.59         & 84.7        & de novo      & 3        & III      \\
SRR5821180 & 48.75         & 98.15       & consensus    & 3        & III      \\
SRR5821181 & 64.45         & 99.3        & consensus    & 3        & III      \\
SRR5821182 & 64.40         & 98.88       & consensus    & 3        & III      \\
SRR5821183 & 115.14        & 95.61       & consensus    & 3        & III      \\
SRR5821184 & 170.72        & 94.11       & de novo      & 3        & III      \\
SRR5821185 & 181.75        & 98.19       & de novo      & 3        & III      \\
SRR5821186 & 246.98        & 96.4        & de novo      & 3        & III      \\
SRR5821187 & 55.62         & 99.74       & consensus    & 3        & III      \\
SRR5821188 & 70.95         & 99.39       & consensus    & 3        & III      \\
SRR5821189 & 82.61         & 99.27       & de novo      & 3        & III      \\
SRR5821190 & 138.58        & 98.81       & consensus    & 3        & III      \\
SRR5821191 & 59.92         & 99.72       & de novo      & 3        & III      \\
SRR5821192 & 40.53         & 36.88       & consensus    & 3        & III      \\
SRR5821193 & 92.08         & 98.9        & de novo      & 3        & III      \\
SRR5821194 & 58.69         & 98.53       & consensus    & 3        & III      \\
SRR5821195 & 127.80        & 99.64       & consensus    & 3        & III      \\
SRR5821196 & 59.30         & 86.62       & de novo      & 3        & III      \\
SRR5821197 & 87.78         & 99.47       & de novo      & 3        & III      \\
SRR5821198 & 185.55        & 99.72       & de novo      & 3        & III      \\
SRR5821199 & 83.55         & 99.62       & consensus    & 3        & III      \\
SRR5821200 & 85.52         & 99.5        & consensus    & 3        & III      \\
SRR5821201 & 129.77        & 94.6        & consensus    & 3        & III      \\
SRR5821202 & 56.60         & 99.81       & consensus    & 3        & III      \\
SRR5821203 & 80.28         & 99.22       & consensus    & 3        & III      \\
SRR5821204 & 68.46         & 95.52       & de novo      & 3        & III      \\
SRR5821205 & 44.45         & 98.53       & consensus    & 3        & III      \\
SRR5821206 & 43.67         & 97.88       & consensus    & 3        & III      \\
SRR5821207 & 78.93         & 99.22       & de novo      & 3        & III      \\
SRR5821208 & 87.45         & 97.72       & consensus    & 3        & III      \\
SRR5821209 & 73.40         & 94.16       & de novo      & 3        & III      \\
SRR5821210 & 55.86         & 91.35       & de novo      & 3        & III      \\
SRR5821211 & 75.53         & 85.6        & consensus    & 3        & III      \\
SRR5821212 & 98.89         & 99.09       & de novo      & 3        & III      \\
SRR5821213 & 84.85         & 95.03       & de novo      & 3        & III      \\
SRR5821214 & 15.33         & 96.28       & de novo      & 3        & III      \\
SRR5821215 & 13.08         & 96.74       & consensus    & 3        & III      \\
SRR5821216 & 45.07         & 98.85       & de novo      & 3        & III      \\
SRR5821217 & 161.65        & 88.94       & consensus    & 3        & III      \\
SRR5821218 & 51.09         & 95.29       & consensus    & 3        & III      \\
SRR5821219 & 84.68         & 99.1        & de novo      & 3        & III      \\
SRR5821220 & 88.26         & 82.64       & de novo      & 3        & III      \\
SRR5821221 & 64.76         & 86.62       & de novo      & 3        & III      \\
SRR5821222 & 93.47         & 97.48       & consensus    & 3        & III      \\
SRR5821223 & 86.50         & 98.99       & de novo      & 3        & III      \\
SRR5821224 & 73.31         & 26.43       & consensus    & 3        & III      \\
SRR5821225 & 68.85         & 98.43       & consensus    & 3        & III      \\
SRR5821226 & 67.75         & 96.67       & consensus    & 3        & III      \\
SRR5821227 & 32.56         & 99.54       & de novo      & 3        & III      \\
SRR5821228 & 38.73         & 86.68       & consensus    & 3        & III      \\
SRR5821229 & 77.18         & 99.69       & consensus    & 3        & III      \\
SRR5821230 & 175.73        & 99.58       & de novo      & 3        & III      \\
SRR5821231 & 100.82        & 99.58       & de novo      & 3        & III      \\
SRR5821232 & 86.89         & 99.47       & consensus    & 3        & III      \\
SRR5821233 & 270.15        & 99.56       & consensus    & 3        & III      \\
SRR5821234 & 76.07         & 99.75       & consensus    & 3        & III      \\
SRR5821235 & 32.78         & 79.78       & consensus    & 3        & III      \\
SRR5821236 & 80.19         & 24.72       & de novo      & 3        & III      \\
SRR5821237 & 50.59         & 97.38       & consensus    & 3        & III      \\
SRR5821238 & 63.56         & 97.63       & de novo      & 3        & III      \\
SRR5821239 & 29.66         & 41.15       & consensus    & 3        & III      \\
SRR5821240 & 62.61         & 94.64       & de novo      & 3        & III      \\
SRR5821241 & 17.52         & 98.03       & consensus    & 3        & III      \\
SRR5821242 & 58.86         & 99.25       & consensus    & 3        & III      \\
SRR5821243 & 50.08         & 93.56       & consensus    & 3        & III      \\
SRR5821244 & 32.67         & 99.09       & consensus    & 3        & III      \\
SRR5821245 & 64.96         & 99.77       & consensus    & 3        & III      \\
SRR5821246 & 104.11        & 90.14       & consensus    & 3        & III      \\
SRR5821247 & 98.64         & 99.73       & consensus    & 3        & III      \\
SRR5821248 & 129.28        & 90.73       & consensus    & 3        & III      \\
SRR5821249 & 45.76         & 93.13       & de novo      & 3        & III      \\
SRR5821250 & 72.54         & 98.88       & de novo      & 3        & III      \\
SRR5821251 & 115.85        & 97.7        & consensus    & 3        & III      \\
SRR5821252 & 60.76         & 94          & consensus    & 3        & III      \\
SRR5821253 & 64.45         & 99.66       & consensus    & 3        & III      \\
SRR5821254 & 0.27          & 98.12       & consensus    & 3        & III      \\
SRR5821255 & 62.53         & 99.55       & de novo      & 3        & III      \\
SRR5821256 & 54.57         & 99.58       & consensus    & 3        & III      \\
SRR5821257 & 34.90         & 99.53       & de novo      & 3        & III      \\
SRR5821258 & 68.64         & 99.6        & consensus    & 3        & III      \\
SRR5821259 & 73.04         & 98.8        & consensus    & 3        & III      \\
SRR5821260 & 54.60         & 99.14       & consensus    & 3        & III      \\
SRR5821261 & 55.54         & 95.5        & de novo      & 3        & III      \\
SRR5821262 & 106.05        & 91.78       & consensus    & 3        & III     
\end{longtable}

\begin{longtable}{@{}lllll@{}}
\caption{Taxonomic profiling results for the amplicon sequencing samples with less than 70\% DENV DNA.}
\label{tab:chap4_s5}\\
\toprule
\multirow{2}{*}{\textbf{Sample}} & \textbf{Bowtie2}   & \multicolumn{3}{c}{\textbf{Kraken2 (minikraken2\_v2 DB)}}        \\* \cmidrule(l){2-5} 
                                 & \textbf{DENV (\%)} & \textbf{Unclassified} & \textbf{Homo sapie} & \textbf{DENV (\%)} \\* \midrule
SRR5821236 & 24.72 & 5.47  & 71.61 & 19.63 \\*
SRR5821224 & 26.43 & 7.01  & 71.06 & 19.58 \\* 
SRR5821192 & 36.88 & 8.12  & 61.78 & 28.73 \\* 
SRR5821239 & 41.15 & 8.29  & 56.43 & 33.84 \\* 
SRR5821167 & 49.19 & 14.79 & 50.16 & 34.38 \\* 
SRR5821166 & 62.03 & 13.72 & 37.77 & 47.97 \\* 
\end{longtable}

\begin{longtable}{@{}llllll@{}}
\caption{Number of raw base pairs, overall alignment rate, in percentage, for the mapping against the DENV database, number of ORFs recovered, and respective serotype and genotype for 78 single-end amplicon sequencing samples.}
\label{tab:chap4_s6}\\ \toprule
Sample     & Raw Megabases & \% DENV DNA & CDS Assembly & Serotype & Genotype \\ \midrule
SRR3539340 & 330365175     & 83.7        & consensus    & I        & 1        \\
SRR3539341 & 317977866     & 66.56       & consensus    & I        & 1        \\
SRR3539342 & 406075245     & 74.2        & consensus    & I        & 1        \\
SRR3539343 & 302220886     & 59.24       & de novo      & I        & 1        \\
SRR3539344 & 424801129     & 83.21       & de novo      & I        & 1        \\
SRR3539345 & 345821429     & 92.58       & de novo      & I        & 1        \\
SRR3539346 & 411918039     & 90.92       & de novo      & I        & 1        \\
SRR3539347 & 411031278     & 90.92       & de novo      & I        & 1        \\
SRR3539348 & 469139944     & 92.45       & de novo      & I        & 1        \\
SRR3539349 & 537372466     & 90.77       & de novo      & I        & 1        \\
SRR3539350 & 401844325     & 90.32       & de novo      & I        & 1        \\
SRR3539351 & 401993816     & 89.76       & de novo      & I        & 1        \\
SRR3539352 & 357846693     & 88.48       & consensus    & I        & 1        \\
SRR3539353 & 412322289     & 82.94       & de novo      & I        & 1        \\
SRR3539354 & 398022772     & 86.07       & consensus    & I        & 1        \\
SRR3539355 & 388552807     & 92.43       & consensus    & I        & 1        \\
SRR3539357 & 351745878     & 88.51       & consensus    & I        & 1        \\
SRR3539358 & 398098393     & 70.74       & de novo      & I        & 1        \\

>>>>

\input{tables/chapter_4/table1}

@@

The accession numbers for the 132 samples, belonging to zika virus (ZKV), chikungunya virus (CHIKV) and yellow fever virus (YFV) amplicon and metagenomic datasets are available as supplemental material (Table S4). As with the amplicon sequencing dataset, the list of Run Accession IDs was obtained with NCBI’s RunSelector and the raw data was downloaded with the GetSeqENA tool (\url{https://github.com/B-UMMI/getSeqENA}).

@@

\input{tables/chapter_4/suptable1}

@@

\input{tables/chapter_4/suptable2}

\input{tables/chapter_4/suptable3}

@@

\input{tables/chapter_4/suptable4}

\input{tables/chapter_4/suptable5}

\input{tables/chapter_4/suptable6}

\input{tables/chapter_4/suptable7}

\input{tables/chapter_4/suptable8}

\input{tables/chapter_4/suptable9}

\input{tables/chapter_4/suptable10}
